PUT YOUR TITLE HERE

### 2023-03-16 paper/manuscript.Rmd
work on figs

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
 library(brms)
library(tidybayes)
library(kableExtra)
library(viridis)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

@@

```{r}
dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))

sub_with_leg <- dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), 
                                              labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |>
  ggplot(aes(x=subfield, fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+
  labs(y="Count", fill="Subjective \n replication \n score")

@@

open <- dat |> mutate(openness=case_when(
  open_mat==1& open_data==1 ~ "Open materials \n Open data",
  open_mat==1 ~ "Open materials \n No open data",
  open_data==1 ~ "No open materials \n Open data",
  T ~ "No open materials \n No open data")) |> 
  ggplot( aes(x=openness |> factor(), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

within <- ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

top_row <- plot_grid(subfield, modal, leg, rel_widths=c(1,.5,.5), nrow=1)
mid_row <- plot_grid(open, within, vignette, rel_widths=c(1,.5,.5), nrow=1)
plot_grid (top_row, mid_row, nrow=2)
```

>>>>

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
 library(brms)
library(tidybayes)
library(kableExtra)
library(viridis)
library(cowplot)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

@@

```{r predictors-graph, out.width="100%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="y-axes are counts of studies in each category, with each subjective replication score. TODO caption here"}
dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))

sub_with_leg <- dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), 
                                              labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |>
  ggplot(aes(x=subfield, fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
    coord_cartesian(ylim=c(0,55), expand=F)+
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())+
  labs(fill="Subjective\nreplication\nscore")

@@

open <- dat |> mutate(openness=case_when(
  open_mat==1& open_data==1 ~ "Open materials \n Open data",
  open_mat==1 ~ "Open materials \n No open data",
  open_data==1 ~ "No open materials \n Open data",
  T ~ "No open materials \n No open data")) |> 
  ggplot( aes(x=openness |> factor(), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
    coord_cartesian(ylim=c(0,55), expand=F)+
  theme(axis.title.x=element_blank(), axis.title.y=element_blank(), legend.position="none")

modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online\n","Same modality\n"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
    coord_cartesian(ylim=c(0,55), expand=F)+
  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")

within <- ggplot(dat, aes(x=ifelse(is_within, "Within \nsubjects", "Between\nsubjects"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  coord_cartesian(ylim=c(0,55), expand=F)+
  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")

vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single \nvignette", "Multiple \nvignettes"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
    coord_cartesian(ylim=c(0,55), expand=F)+
  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")

top_row <- plot_grid(subfield, within, vignette, rel_widths=c(1, .6, .6), nrow=1)
mid_row <- plot_grid(open,  modal, leg, rel_widths=c(1.2, .6, .25), nrow=1)
plot_grid (top_row, mid_row, nrow=2)
```
